### 2021-02-08 paper/introduction.tex
Update introduction and motivation.

% setting
The first wave of the Covid-19 pandemic prompted strict lockdowns and restrictions
across the world.
At large social and economic costs, these strict measures were able to suppress the
spread of the disease and allowed governments to relax restrictions over the summer.
Governments were more hesitant and imposed less restrictive policies when infections
started to soar again in the fall.
For example, Germany imposed a ``lockdown-light'' in November, closing fewer businesses
than in spring and leaving schools open. Mobility data also showed that individuals
reduced their mobility much less than during the first lockdown.

\textcolor{red}{Add image of Google Mobility reductions!}

% challenge
The less restrictive lockdown led only to a stagnation of cases and led many experts
\textcolor{red}{(Cite No-Covid, Zero-Covid, Leopoldina, Lancet...)} to call for a
strict lockdown to bring cases back to very low levels, such as single digit incidences.
These calls have received additional attention since new and more contagiuos variants
have emerged in several countries and increased the urgency to reduce transmission
dynamics and increased awareness for the mutagenic potential of high incidences.
\textcolor{red}{Add citations!}

However, epidemiological models are not suited to advise which combination of policies
would be able to bring infections down to sustainable levels.
As they have not been designed to predict the effects of fine-grained policies,
they need to be extended for each new policy proposal.
Nor can they show the trade-offs, substitutability or complementarity of policies.

@@

    \item Policies can be implemented as shutting down contact types entirely or
          partially. The reduction of contacts can be random or systematic, e.g., to
          allow for essential workers.

    \item Infection probabilities vary across contact types and reflect properties of
          the contact like the location (indoor/outdoor) and the kind of interaction
          (duration, physical contact). The probabilities are independent from the
          number of contacts and thus policy-invariant.

    \item The model achieves a good fit on German data of infection rates even if only
          the infection probabilities are fit to the data and the remaining parameters
          are calibrated from the medical literature and datasets on contact
          frequencies.

@@

More details about the German model as well as applications to currently discussed
German policies can be found in \citet{Dorn2020a}.
\textcolor{red}{Update citation to home office report.}

In Section~\ref{sec:literature_review}, we give a short overview of epidemiological
models. We continue with a detailed description of our model in Section~\ref{sec:model}
and proceed with a description of model parameters and the estimation in
Section~\ref{sec:calibration_and_estimation}. The model is validated in
Section~\ref{sec:model_validation} by assessing the in-sample fit for reported
infections from August to October and by comparing the out-of-sample fit for the period
from November until the beginning of Christmas for different lockdown scenarios. We
conclude in Section~\ref{sec:conclusion}.

>>>>

% setting
The first wave of the Covid-19 pandemic prompted strict lockdowns and restrictions
across the world.
At large social and economic costs, these strict measures were able to suppress the
spread of the disease in many countries and allowed governments to relax restrictions
over the summer.
When infections started to soar again in the fall, governments were more hesitant
and imposed less restrictive policies.
For example, Germany imposed a ``lockdown-light'' in November, closing fewer businesses
than in spring and leaving schools open.

% challenge
The less restrictive lockdowns proved insufficient to stop the second wave, leading
many experts to call for a strict lockdown to bring cases back to very low levels,
such as single digit incidences (for example \cite{Priesemann2021}).
These calls have received additional attention since new and more contagiuos variants
have emerged in across the globe \citep{Duong2021} and increased the urgency to
reduce transmission dynamics and increased awareness for the mutagenic threat posed by
high incidences.
Given the importance to bring down and maintain low infection numbers until
vaccinations reach herd immunity levels, it is paramount for policy makers and the
public to understand the effectiveness and trade-offs involved in different policies.

However, epidemiological models are not suited for this task.
As they have not been designed to predict the effects of fine-grained policies,
they need to be extended for each new policy proposal.

@@

    \item Policies can be implemented as shutting down contact types entirely or
          partially. The reduction of contacts can be random or systematic. For example,
          it is possible to implement A/B schooling where only one half of each class
          attends and the attending half switches on a weekly bases.

    \item Infection probabilities vary across contact types and reflect properties of
          the contact like the location (indoor/outdoor) and the kind of interaction
          (duration, physical contact). The probabilities are independent from the
          number of contacts and, thus, policy-invariant.

    \item The model achieves a good fit on German data of infection rates even if only
          the infection probabilities are fit to the data and the remaining parameters
          are calibrated from the medical literature and datasets on contact
          frequencies and mobility reductions.

@@

More details about the German model as well as applications to currently discussed
German policies can be found in \citet{Dorn2020a, Gabler2020, Gabler2021}.

The report proceeds as follows: In Section~\ref{sec:literature_review}, we give a
short overview of epidemiological models.
We continue with a detailed description of our model in Section~\ref{sec:model}
and proceed with a description of model parameters and the estimation in
Section~\ref{sec:calibration_and_estimation}. The model is validated in
Section~\ref{sec:model_validation} by assessing the in-sample fit for reported
infections from August to October and by comparing the out-of-sample fit for the period
from November until the beginning of Christmas for different lockdown scenarios. We
conclude in Section~\ref{sec:conclusion}.
